msc dissertation

### 2021-07-20 msc dissertation code.Rmd
latest

#replace condition control = 0 treatment = 1
pennystudy2r1["condition"][pennystudy2r1["condition"] == 1] <- 0
pennystudy2r1["condition"][pennystudy2r1["condition"] == 2] <- 1

>>>>

#re-code condition control = 0 treatment = 1
pennystudy2r1["condition"][pennystudy2r1["condition"] == 1] <- 0
pennystudy2r1["condition"][pennystudy2r1["condition"] == 2] <- 1
